---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Generative-aRt

<!-- badges: start -->
<!-- badges: end -->

This repository is my attempt at generative art. Very much still a working progress, check back in 30 years when I'm much more skilled`r emo::ji("poop")` 


## 1. Random walk 
  - Motivation: to create a hex sticker image for [PalCreatoR](https://github.com/GenChangHSU/PalCreatoR) 
  - I first used [`create_pal`](https://genchanghsu.github.io/PalCreatoR/reference/create_pal.html) to generate color for 2 separate images, which I will use to color the paths of my random walk
  - The random walk algorithm I wrote is really simple:
    1. Setup starting points by drawing randomly from normal distribution 3 times for each of the x, y, z axes
    2. Step 1 is repeated, depending on how many __"walks"__ one wishes to make
    3. Every __step__ has a total of 3 possibilities: i) move back (-1), ii) don't move (0), or iii) move forward (+1) and the probability for any one of the 3 possibility is the same. So steps are drawn from this pool of possibilities with the number of times equal to how many __steps__ one wishes to take
    4. Just to make it more fun, one can modify the __step size__ that each walk can take by drawing from either a uniform distribution or exponential distribution 
    5. For demonstration, I created 2 separate walking scenarios, where one set of walks has more __"more walks"__ and __"less steps"__ and another with "less walks" and "more steps"
    6. Each set of walks was color coded by each of the color palette, with each walk within each set assigned randomly to one of the colors in the palette
  - [script](https://github.com/jiaangou/Generative-aRt/blob/master/random-walk-art.R)

```{r, fig.width = 4}
magick::image_read('random-walk-static.jpg')
```


```{r, fig.width = 4}
magick::image_read('random-walks.gif')
```


## 2. 1D-Cellular Automaton
  - Motivation: I've recently become obsessed with *complexity science* which I'll admit is a loaded term. But the gist of it is the phenomenon in which complex structures and patterns can emerge from (relatively) simple rules. Cellular automatons are the perfect toys to play around with these *rules*

